---
title: "My R packages"
author: Laurent Gatto
---

Latest udate: `r date()`

This post provides a short summary of some packages I develop,
maintain or actively contribute to. Some packages are quite mature,
other early stages.  The final table provides the package version in
the respective repositories.  For an up-to-date version of this
document, see https://lgatto.github.io/my-r-packages/.


```{r dopkg pkgs, echo=FALSE}
library("BiocStyle")
library("biocpkgs")
library("knitr")
pkgs <- ghuser <- rep <- c()
do_pkg <- function(pkg = NULL, user = "lgatto", repo = "software") {
	stopifnot(!is.null(pkg))
	pkgs <<- append(pkgs, pkg)
	ghuser <<- append(ghuser, user)
	rep <<- append(rep, repo)
	desc <- packageDescription(pkg)$Description
	desc <- gsub("\\t +", "", desc)
	desc <- gsub("\\\n +", " ", desc)
	writeLines(desc)
}
```

# `r Biocannopkg("RforProteomics")`

```{r f4p, echo=FALSE, results="asis", error=FALSE}
do_pkg("RforProteomics", "lgatto", "experiment")
```

# `r Biocpkg("mzR")`

```{r mzr, echo=FALSE, results="asis", error=FALSE}
do_pkg("mzR", "sneumann", "software")
```


# `r Biocpkg("MSnbase")`

```{r msnbase, echo=FALSE, results="asis", error=FALSE}
do_pkg("MSnbase")
```


# `r Biocpkg("pRoloc")`

```{r proloc, echo=FALSE, results="asis", error=FALSE}
do_pkg("pRoloc")
```


# `r Biocpkg("pRolocGUI")`


```{r prolocgui, echo=FALSE, results="asis", error=FALSE}
do_pkg("pRolocGUI", "ComputationalProteomicsUnit", "software")
```

# `r Biocexptpkg("pRolocdata")`

```{r prolocdata, echo=FALSE, results="asis", error=FALSE}
do_pkg("pRolocdata", "lgatto", "experiment")
```


# `r Biocpkg("rols")`


```{r rols, echo=FALSE, results="asis", error=FALSE}
do_pkg("rols")
```

# `r Biocpkg("rpx")`

```{r rpx, echo=FALSE, results="asis", error=FALSE}
do_pkg("rpx")
```

# `r Biocpkg("hpar")`

```{r hpar, echo=FALSE, results="asis", error=FALSE}
do_pkg("hpar")
```

# `r Biocpkg("Pbase")`

```{r pbase, echo=FALSE, results="asis", error=FALSE}
do_pkg("Pbase", "ComputationalProteomicsUnit", "software")
```

# `r Biocpkg("ProteomicsAnnotationHubData")`

```{r pahd, echo=FALSE, results="asis", error=FALSE}
do_pkg("ProteomicsAnnotationHubData")
```

# `r Biocpkg("qcmetrics")`

```{r qcm, echo=FALSE, results="asis", error=FALSE}
do_pkg("qcmetrics")
```

# `r Biocpkg("synapter")`

```{r synapter, echo=FALSE, results="asis", error=FALSE}
do_pkg("synapter")
```

# `r Biocexptpkg("synapterdata")`

```{r snapterdata, echo=FALSE, results="asis", error=FALSE}
do_pkg("synapterdata", NA_character_, "experiment")
```

# `r Biocpkg("ProtGenerics")`

```{r protgenerics, echo=FALSE, results="asis", error=FALSE}
do_pkg("ProtGenerics")
```

# `r Biocpkg("yaqcaffy")`

```{r yaqc, echo=FALSE, results="asis", error=FALSE}
do_pkg("yaqcaffy", NA_character_, "software")
```

# `r Biocpkg("sequences")`

```{r sequences, echo=FALSE, results="asis", error=FALSE}
do_pkg("sequences", "lgatto", "cran")
```

# `r Githubpkg("lgatto/biocpkgs")`

```{r biopcks, echo=FALSE, results="asis", error=FALSE}
do_pkg("biocpkgs", "lgatto", NA_character_)
```

# `r Githubpkg("lgatto/yagop")`


```{r yagop, echo=FALSE, results="asis", error=FALSE}
do_pkg("yagop", "lgatto", NA_character_)
```

# Package versions {-}

```{r table, pkgtab, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
ghpkgs <- paste(ghuser, pkgs, sep = "/")
names(ghpkgs) <- pkgs
ghpkgs[is.na(ghuser)] <- NA
ghv <- sapply(ghpkgs,
              function(x) ifelse(is.na(x),
               "Not available on Github",
               githubpkgversion(x)))
repv <- sapply(seq_along(rep),
               function(i) {
                 if (is.na(rep[i])) "Not in any package repository"
                 else if (rep[i] == "cran") paste("CRAN", cranpkgversion(pkgs[i]))
                 else paste("Bioconductor",
                             biocpkgversion(pkgs[i], "release", rep[i]),
                             "(release)",
                             biocpkgversion(pkgs[i], "devel", rep[i]),
                             "(devel)")})

tab <- data.frame(package = pkgs, repository = repv, GitHub = ghv,
				  row.names = NULL)
knitr::kable(tab)
```
