---
title: "My R packages"
author: 
- name: Laurent Gatto
abstract: >
 This post provides a short summary of all packages I develop, maintain or 
 actively contribute to. The final table provides the package version in 
 the respective repositories. For an up-to-date version of this document, 
 see https://lgatto.github.io/my-r-packages/.
output:
  BiocStyle::html_document:
    toc_float: true
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

Latest udate: `r date()`

```{r pkgs, echo=FALSE}
library("BiocStyle")
library("biocpkgs")
library("knitr")
pkgs <- ghuser <- rep <- c()
do_pkg <- function(pkg = NULL, user = "lgatto", repo = "software") {
    stopifnot(!is.null(pkg))
    pkgs <<- append(pkgs, pkg)
    ghuser <<- append(ghuser, user)
    rep <<- append(rep, repo)
    desc <- packageDescription(pkg)$Description
    desc <- gsub("\\t +", "", desc)
    desc <- gsub("\\\n +", " ", desc)
    writeLines(desc)
}
```

# `r Biocannopkg("RforProteomics")`

```{r, echo=FALSE, results="asis", error=FALSE}
do_pkg("RforProteomics", "lgatto", "experiment")
```

# `r Biocpkg("mzR")` 

```{r, echo=FALSE, results="asis", error=FALSE}
do_pkg("mzR", "sneumann", "software")
```


# `r Biocpkg("MSnbase")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("MSnbase")
```

# `r Biocpkg("pRoloc")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("pRoloc")
```

# `r Biocpkg("pRolocGUI")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("pRolocGUI", "ComputationalProteomicsUnit", "software")
```

# `r Biocexptpkg("pRolocdata")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("pRolocdata", "lgatto", "experiment")
```
		 
# `r Biocpkg("rols")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("rols")
```

# `r Biocpkg("rpx")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("rpx")
```

# `r Biocpkg("hpar")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("hpar")
```

# `r Biocpkg("Pbase")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("Pbase", "ComputationalProteomicsUnit", "software")
```

# `r Biocpkg("ProteomicsAnnotationHubData")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("ProteomicsAnnotationHubData")
```

# `r Biocpkg("qcmetrics")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("qcmetrics")
```

# `r Biocpkg("synapter")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("synapter")
```

# `r Biocexptpkg("synapterdata")`

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("synapterdata", NA_character_, "experiment")
```

# `r Biocpkg("ProtGenerics")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("ProtGenerics")
```

# `r Biocpkg("yaqcaffy")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("yaqcaffy", NA_character_, "software")
```

# `r Biocpkg("sequences")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("sequences", "lgatto", "cran")
```

# `r Githubpkg("lgatto/biocpkgs")` 

```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("biocpkgs", "lgatto", NA_character_)
```

# `r Githubpkg("lgatto/yagop")` 


```{r echo=FALSE, results="asis", error=FALSE}
do_pkg("yagop", "lgatto", NA_character_)
```

# Package versions {-}

```{r pkgtab, echo=FALSE, error=FALSE}
ghpkgs <- paste(ghuser, pkgs, sep = "/")
names(ghpkgs) <- pkgs
ghpkgs[is.na(ghuser)] <- NA
ghv <- sapply(ghpkgs,
              function(x) ifelse(is.na(x),
                                 "Not available on Github",
                                 githubpkgversion(x)))
repv <- sapply(seq_along(rep),
               function(i) {
                   if (is.na(rep[i])) "Not in any package repository"
                   else if (rep[i] == "cran") paste("CRAN", cranpkgversion(pkgs[i]))
                   else paste("Bioconductor",
                              biocpkgversion(pkgs[i], "release", rep[i]),
                              "(release)",
                              biocpkgversion(pkgs[i], "devel", rep[i]),
                              "(devel)")
               })


tab <- data.frame(package = pkgs, repository = repv, GitHub = ghv,
                  row.names = NULL)
knitr::kable(tab)
```
